---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# trapDetect
<!-- badges: start -->
<<<<<<< HEAD
=======
  [![R-CMD-check](https://github.com/dangladish/trapDetect/workflows/R-CMD-check/badge.svg)](https://github.com/dangladish/trapDetect/actions)
>>>>>>> 18ed2c71958bd5cde2a6e216e3c46af6bc6e66bc
[![R-CMD-check](https://github.com/dangladish/trapDetect/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/dangladish/trapDetect/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of trapDetect is to provide the functionality to simulate the spread of individuals over a given area (such as an orchard or block), and provide the tools to determine the probability of detecting a pest using various detection functions.  

## Installation

You can install trapDetect from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("dangladish/trapDetect")
```

Please note that trapDetect is in early development and likely will change significantly.

## The main function: calc_escape_prob()

The main function is `calc_escape_prob()` which simulates the spread of a population of individuals using the `sim_spread()` function if not provided, and then determines the probability of detecting an individual for a given trap configuration using `p_detect_one()`.  There are a number of optional arguments in `calc_escape_prob()` which the user can set for their own purposes.  A basic example can be run using the following code:

```{r example}
library(trapDetect)
calc_escape_prob()
```

## Contact
For all inquires regarding the `trapDetect` R package, please contact: Dan Gladish (<Dan.Gladish@data61.csiro.au>).  

