---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# trapDetect
<!-- badges: start -->
[![R-CMD-check](https://github.com/dangladish/trapDetect/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/dangladish/trapDetect/actions/workflows/R-CMD-check.yaml)
<!-- badges: end --> 

The goal of trapDetect is to provide the functionality to simulate the spread of individuals over a given area (such as an orchard or block), and provide the tools to determine the probability of detecting a pest using various detection functions.   

## Installation

You can install trapDetect from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("dangladish/trapDetect")
```

Please note that `trapDetect` is in development.

## The main function: `calc_escape_prob()`

The main function is `calc_escape_prob()` which simulates the spread of a population of individuals using the `sim_spread()` function if not provided, and then determines the probability of detecting an individual for a given trap configuration using `p_detect_one()`.  There are a number of optional arguments in `calc_escape_prob()` which the user can set for their own purposes.  A basic example can be run using the following code:

```{r example}
library(trapDetect)
calc_escape_prob()
```

## Simulate Capture: `sim_capture()`

The `sim_capture()` focuses on trap catch counts rather than probability of capture.  This function acts in a similar manner as `sim_spread()` but needs information about detection devices.  This can be in the form of trap locations or number of traps in the space.  If number of traps is specified, traps are arranged in a grid covering the block as much as possible.  It is recommended to run `sim_capture()` multiple times for uncertainty estimates.

## Contact
For all inquires regarding the `trapDetect` R package, please contact: Dan Gladish (<Dan.Gladish@data61.csiro.au>).  
